DISTRIBUTED CROSS-RELATION-BASED FREQUENCY-DOMAIN\\ BLIND SYSTEM IDENTIFICATION USING ONLINE-ADMM

### 2022-05-06 paper.tex
minor change and remove pdf

The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)).
The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
\autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median (30 Monte-Carlo runs) where the averaged NPM of \(100\) frames after convergence is plotted.
It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifiability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.

>>>>

The first simulation evaluates the performance using randomly generated impulse responses of length \(L=64\) under different signal-to-noise ratios (SNR) on a 5-node network (5-channel system, \(M=5\)) with a ring topology where each node transmits its signal information to one neighbor.
The impulse responses are drawn from a zero-mean Gaussian distribution with unit variance, and the signal is \(8 \times 10^{5}\) samples of WGN to ensure convergence of all algorithms.
The step sizes are hand tuned for similar convergence speed: \(\mu_{\text{MCQN}}=0.5,\, \mu_{\text{NMCFLMS}}=0.4,\, \mu_{l_p-\text{NMCFLMS}}=0.3,\, \mu_{\text{ADMM}}=0.6,\, \rho=1,\,\eta=0.98 \).
\autoref{fig:perf_eval:NPM_over_time_SNR10} shows the median NPM (30 Monte-Carlo runs) over frame index \(m\).
\autoref{fig:perf_eval:NPM_over_SNR_L64_M5} shows the median (30 Monte-Carlo runs) where the averaged NPM of \(100\) frames after convergence is plotted.
It is observable that the proposed algorithm yields a lower steady-state NPM than the compared NMCFLMS, RNMCFLMS, and \(l_p\)-RNMCFLMS algorithms.
The choice to present the median is based on the fact that randomly generated impulse responses may have close common zeros diminishing identifiability (for all algorithms) \cite{naylorNearCommonZerosBlind2008}, here then considered outliers.
